Implementing Real-Time Transport Services over an Ossified Network

### 2016-05-23 paper.tex
Related work

The Minion protocol suite \cite{nowlan:2012:minion} includes uTCP, a
protocol that uses TCP as a substrate to provide an unordered,
message-oriented service to applications. While this enables many of
the transport services described in Section \ref{sec:services}, support for
partial reliability, deadlines, and dependencies is not provided.
Time-Lined TCP (TLTCP) \cite{mukherjee:2000:timelines} similarly provides a
message-oriented service, but allows applications to attach a time-line
to messages. Messages are (re-)transmitted as under standard TCP within
their time-line, after which they are discarded. The mechanism by which
this service is provided (i.e., the introduction of gaps in the sequence
space) reduces deployability.

\todo{QUIC}

\todo{SPUD}

\todo{WebRTC data channel - SCTP over UDP}

\todo{RFC6773 - DCCP over UDP}

>>>>

Related changes to TCP are made by Minion protocol \cite{nowlan:2012:minion},
that uses TCP as a substrate to provide an unordered, message-oriented
service to applications, enabling some of the transport services described
in Section \ref{sec:services}, but without support for partial reliability,
deadlines, and dependencies.
Time-Lined TCP (TLTCP) \cite{mukherjee:2000:timelines} similarly provides a
message-oriented service, but allows applications to attach a time-line
to messages. Messages are (re-)transmitted as under standard TCP within
their time-line, after which they are discarded. The mechanism by which
this service is provided (introducing gaps in the sequence space) hinders
deployment.

QUIC \cite{draft-tsvwg-quic-protocol-02} demonstrates that similar services
can be provided by a new protocol running over UDP, while \cite{RFC6773} and
\cite{draft-ietf-rtcweb-data-channel-13} demonstrate that existing protocols,
DCCP and SCTP, can also be effectively tunnelled over UDP. Fallback to TCP
is discussed in this paper, and on our previous work \cite{mcquistin2016hollywood}.
